---
title: "Alcohol vs Seat choice"
author: "Emraida S.Ortanez"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
people in the back are drinking more 
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The first plot is of Box plot. Here it gives an idea of the distribution of the data .  
Now from the first boxplot, there seems to be high spread   
There are two outliers in this plot and median value of the alcohol lies close to 5   
The first boxplot is positively skewed.
The second boxplot is less spreaded . 
The median is around 0  
But the values of quartiles and median are very close to each other   
In the third plot, there are many outliers   
The distribution of second and third plot is similar but only number of outliers in third plot is more   

## Numerical Summarys 
# Numerical results

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
```{r}
plot(TukeyHSD(model1))
```
In the second plot, this is the plot of 95% confidence interval of the difference    
Now look at the first line, it is comparison of Front and back values, the whole confidence interval is less than   
zero meaning that the front values are less as compared to Back Values .  
Second line is of back and middle, here again the CI lies below 0 means   
that the values of the back is larger than middle values   
The third line is of middle front, this lies partly above the 0 and partly below the zero    
Meaning that the values of both these seats are equal in CI   

## Conclusions


